The value of intermediation

### 2022-09-13 src/presentation/presentation.qmd
Add multiple platforms extension

>>>>

::: {.column width="45%"}
Imagine that

  - There are $m$ platforms
  - They are perfect substitutes
:::

::: {.column .fragment width="5%"}
:::

::: {.column .fragment width="45%"}
That is, 
$$
   v(S) = \begin{cases}
      0  \; \text{ if } P_i \notin S \; \forall i \\
      f\left(\frac{\#_A(S)}{n}\right)
   \end{cases}
$$
:::

::: {.notes}
 - Probabilistic interpretation: the platform has to be the first one in order to have any additional value
 - As the number of platforms increases, the *total value* they obtain decreases, and the total value firms obtain increases
:::

::: {#prp-multiple-platforms .fragment}
## Multiple platforms
The limit of the Shapley-value (as $n \to \infty$) of each player of type $P$ is
$$
\begin{aligned}
   \varphi_{P_i}^{\infty, m} = \int_0^1 (1-t) ^ {m-1} f(t) \mathrm{d}t .
\end{aligned}
$$
:::
